%------------------------
% Resume Template
% Author: JAYABRATA PRAMANIK
% Github: https://github.com/Jayabrata18/resume
% License: MIT
%------------------------
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{hyperref}
\RequirePackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{%
  \item\small{\textbf{#1}: #2 \vspace{-2pt}}%
}

\newcommand{\resumeItemWithoutTitle}[1]{%
  \item\small{{\vspace{-2pt}}}%
}

\newcommand{\resumeSubheading}[4]{%
  \vspace{-1pt}\item%
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}%
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}%
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=15pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Jayabrata Pramanik}} & Email: \href{mailto:jayabrata180402@gmail.com}{jayabrata180402@gmail.com}\\
 \vspace{2pt}
  \href{https://jayabratapramanik.me/}{Portfolio: jayabratapramanik.me} & Mobile: +91-9091392947 \\
  \href{https://github.com/Jayabrata18/}{\large Github: github.com/Jayabrata18}  & \href{https://twitter.com/Jayabrata22/}{Twitter: @jayabrata22}\\
  \href{https://leetcode.com/jayabrata18/}{LeetCode: jayabrata18} & \href{https://www.linkedin.com/in/jayabrata-pramanik/}{Linkedin: Jayabrata Pramanik}
\end{tabular*}
\faMapMarker~Bengaluru

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{\normalsize Techno Main SaltLake (CGPA: 8.48)}{Kolkata, India}
{\normalsize Bachelor of Technology - Electronics and Communication Engineering}{November 2020 – July 2024}
{\scriptsize \textit{ \large {\newline{}\textbf{Courses:} Digital Signal Processing, Analog Communication, Digital Communication, Digital Circuits, Network Theory, Operating Systems, Data Structures and Algorithms, Analysis Of Algorithms, Computer Networks, Object-Oriented Programming, DBMS, ITC.}}}
\resumeSubHeadingListEnd

\vspace{-12pt}
\section{Skills Summary}
\resumeSubHeadingListStart
\resumeSubItem{\large Languages}{\large JavaScript, Typescript, Java, Go, Solidity, Rust}
\vspace{3pt}
\resumeSubItem{\large Frameworks}{\large React, React Native, Nestjs, Threejs, Web3js, Etherjs, Tailwind CSS, Express, Nextjs, Sanity.io, Firebase, Nodejs}
\vspace{3pt}
\resumeSubItem{\large Database}{\large MongoDB, PostgreSQL, MySQL, Redis}
\vspace{3pt}
\resumeSubItem{\large Infrastructure}{\large Docker, Kubernetes, Git, GitHub Actions, AWS, Elasticsearch, }
\vspace{3pt}
\resumeSubItem{\large Platforms}{\large Linux, Windows, AWS, GCP, Azure}
\vspace{3pt}
\resumeSubHeadingListEnd
\vspace{-12pt}

%-----------WORK EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Full Stack Developer Intern}
{INFOMATICAE SOLUTIONS PVT. LTD}
{January 2024 - Present}
{Mumbai}
\vspace{-5pt}
{\large
\begin{itemize}
\item \textbf{Developing} front-end and backend, \textbf{maintaining} full-stack websites to ensure \textbf{optimal functionality} and \textbf{exceptional user experience}.
  \item \textbf{Crafted} an Internal Expense Tracker Website and App, \textbf{streamlining} expense management processes.
  \item \textbf{Collaborating} with cross-functional teams to meticulously define project requirements, scope, and deliverables, ensuring perfect alignment with client goals and expectations.
  \item \textbf{Technologies:} Proficiently utilizing \textbf{React}, \textbf{Nestjs}, \textbf{PostgreSQL}, \textbf{MongoDB}, \textbf{Docker}, and \textbf{GitHub} to deliver robust and scalable solutions.
\end{itemize}
}
\resumeSubheading
{Full Stack Developer \& Blockchain Developer}
{KNW Technologies}
{June 2022 - July 2023}
{Remote}
\vspace{-5pt}
{\large
\begin{itemize}
\item \textbf{Developed and meticulously maintained} full-stack websites, ensuring \textbf{optimal functionality} and \textbf{exceptional user experience}.
\item \textbf{Pioneered} the creation of a blockchain-based NFT minting website, \textbf{implementing} smart contracts and \textbf{rigorous security measures} for digital asset management.
\item \textbf{Engineered} and \textbf{deployed} web scraping tools to gather valuable data for clients, \textbf{enhancing} their decision-making processes.
\item \textbf{Collaborated} with cross-functional teams to \textbf{meticulously define} project requirements, scope, and deliverables, \textbf{ensuring} alignment with client goals.
\end{itemize}
}
\resumeSubheading
{Founder {\href{https://www.healthocares.com/}{\normalsize (healthocares.com)}}}
{Self-employed}
{January 2023 - Present}
{Remote}
\vspace{-8pt}
{\large
\begin{itemize}
\item \textbf{Conceptualized and spearheaded} the development of a website to provide people with \textbf{authoritative information} about health and health workers such as Doctors, Nurses, Medicine shops, Government Programs, Awareness Programs, and Free Medical Camps.
\item \textbf{Engineered} a multilingual website to \textbf{extend outreach} and \textbf{connect} with a \textbf{wider audience}.
\end{itemize}
}

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\vspace{6pt}
\resumeSubItem{\large Microservices-based Food Delivery Backend}{\href{https://github.com/Jayabrata18/Food-delivery-app-microservice-backend}{\large \faGithub}}
{\large
\begin{itemize}
\item \textbf{Developed} a robust and scalable microservices-based backend for a food delivery platform using \textbf{NestJS} with a monorepo architecture, allowing for shared codebase management and improved development efficiency.
\item \textbf{Designed} an HTTP API Gateway to handle all routes, ensuring a centralized entry point for all requests and \textbf{implemented} role-based access control to manage secure authentication and authorization for different user roles.
\item \textbf{Created} distinct microservices for \textbf{User}, \textbf{Admin}, \textbf{Restaurant}, \textbf{Order}, and \textbf{Delivery Agent} functionalities, each responsible for its own domain logic, promoting modularity and ease of maintenance.
\item \textbf{Utilized} \textbf{PostgreSQL} as the primary database to provide \textbf{reliable}, \textbf{consistent}, and \textbf{efficient} data storage and retrieval, ensuring data integrity and performance.
\item \textbf{Containerized} the entire application using \textbf{Docker}, enabling \textbf{consistent} environments across different stages of development, testing, and production, which simplifies deployment and scaling processes.
\item \textbf{Implemented} \textbf{NATS} as a messaging system to \textbf{facilitate} efficient communication between microservices.
\item \textbf{Deployed} the application on \textbf{AWS EC2} to ensure \textbf{high availability} and \textbf{seamless scalability}.
\item \textbf{Set up} \textbf{GitHub Actions} for a \textbf{streamlined} continuous integration and continuous deployment (\textbf{CI/CD}) pipeline.
\end{itemize}

}

\vspace{-6pt}
\resumeSubItem{\large Doctor Booking and Video Consulting Website}{\href{https://github.com/Jayabrata18/mlh_diversion2k23_hackathon}{\large \faGithub}}
{\large
\begin{itemize}
    \item \textbf{Developed} a comprehensive full-stack website empowering users to seamlessly book doctor appointments and engage in video consultations.
    \item \textbf{Implemented} an innovative feature enabling automatic dispatch of video call links to users at their scheduled appointment time, enhancing convenience and accessibility.
    \item \textbf{Utilized} \textbf{React}, \textbf{Axios}, and \textbf{Material-UI} to craft a polished and intuitive frontend interface, ensuring an engaging user experience.
    \item \textbf{Employed} \textbf{Node.js} and \textbf{Express} on the backend to efficiently manage appointment scheduling and video call functionalities, ensuring robust performance and reliability.
    \item \textbf{Leveraged} \textbf{MongoDB} to securely store user and appointment data, maintaining confidentiality and data integrity.
    \item \textbf{Integrated} \textbf{Socket.io} to enable seamless real-time communication between users and doctors, fostering effective and immediate interaction.
    \item \textbf{Ensured} compliance with industry standards and best practices to deliver a secure, scalable, and user-centric solution, meeting the evolving needs of healthcare services.
\end{itemize}

}

\vspace{-8pt}
\resumeSubItem{\large Quiz App}{\href{https://github.com/Jayabrata18/Quiz-App}{\large \faGithub}}
{\large
\begin{itemize}
    \item \textbf{Developed} a dynamic quiz app offering users a challenging and interactive experience.
    \item \textbf{Integrated} an external API to fetch diverse and engaging quiz questions, enriching the app content and user engagement.
    \item \textbf{Enabled} users to participate in quizzes and receive scores based on 10 questions, with no question repetition, fostering engagement and competition.
    \item \textbf{Implemented} \textbf{React Native CLI} to ensure platform-native performance and smooth user interactions, delivering a seamless quiz-taking experience.
\end{itemize}

}
\resumeSubHeadingListEnd

%-----------Hackathons-----------------
\section{Hackathons}
\begin{description}[font=$\bullet$]
\item {\normalsize Participated in various MLH online hackathons and won track prizes.}
\vspace{-5pt}
\item {\normalsize Attended in-person MLH Diversion-2023 in Kolkata.}
\vspace{-5pt}
\item {\normalsize Attended in-person Solana Hacker House Bengaluru.}
\vspace{-5pt}
\end{description}
\vspace{-5pt}
{\hfill \textit{Last updated on 22/06/2024}}

\end{document}
